---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

xmr <-
  function(x, index){
    require(data.table)
    require(ggplot2)
    
    lag <- data.table::shift(x, n=1)
    mr <- abs(x-lag)
    mean_s <- mean(x)
    mean_mr <- mean(na.omit(mr))
    
    UCL <- mean_s + (3*mean_mr / 1.128)
    LCL <- mean_s - (3*mean_mr / 1.128)
    
    rule <- ifelse(x>UCL,1,ifelse(x<LCL,3,2))
    
    ggplot(data.frame(index, x), aes(x=index, y=x))+
      geom_point(aes(col=factor(rule)))+
      geom_line()+
      geom_hline(yintercept=mean_s, col="black", linetype="dashed")+
      geom_hline(yintercept=UCL, col="dodgerblue2")+
      geom_hline(yintercept=LCL, col="purple")
  }



```

# Quick SPC messing

<!-- badges: start -->
<!-- badges: end -->

This is a quick repository whilst I was messing around with building an XmR after someone asked for it.
THere are tow scripts, one which is a working script `xmr`, and the other is a function that can be used on a `data.frame` where we have and index such as data and a value.

It's just a shell, and I've only added a single rule for outside control limits, but you'd add more in real use.

### Here's how to use it:

Firstly, create a data set at random with a 'seed' so it's the same.  You'd replace this with your real data.
```{r example}
set.seed(123)

dt <- data.frame(id = seq(30),
                 val = rnorm(30, 30,5))

```

I'm going to force a couple of outliers here so you can see them:

```{r outlier}
dt$val[10] <- dt$val[10] +10
dt$val[11] <- dt$val[11] +20

```


Now let's plot it:

```{r xmrplot}
xmr(x=dt$val, index=dt$id)
```


